Computational Methods for Principle Component Analysis Applied to Genotype Data

### 2018-06-17 doc/paper/paper.tex

\usepackage{epsfig} \usepackage[margin=1.5in]{geometry}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[capitalise]{cleveref}
\usepackage{verbatim}
\usepackage{float}

@@

We also applied the four methods
to study the UK Biobank data \citep{sudlow2015uk},
which consists of 490,000 middle- or elderly-aged individuals
in the United Kingdom.
Our reference samples
are from the 1000 Genomes Project \citep{10002015global},
which collected 2500 samples from Europe, Africa, East Asia, South Asia, and America.
(Individuals whose children are also in the data were removed.)
The reference and the study samples
have 145,000 SNPs in common.
After we predicted the PC scores and ethnic groups
of the study samples,
we selected the study samples predicted to by Europeans
and applied PCA to them
by using the European reference samples only.

@@

Simulation study

Runtimes vs ref size
Distance to ADP vs ref size
Distance to geo center vs ref size
PC1 vs PC2, 5 x 3 grid (uncolored study samples)

UK Biobank

500 samples, 4 methods
All continents
European only
misclassification rate compared to ADP
distance to ADP

all samples, 3 methods
same as above

The predicted PC scores are shown in \Cref{fig:n1000} and \Cref{fig:ukb}.
For the comparison of the runtimes and accuracy for different reference and sample sizes for the simulated data,
see \Cref{fig:nChg} and \Cref{fig:mChg}.
For comparing the methods for the real-life data, see \Cref{tbl:ukb}.

@@

For the real-life datasets (\Cref{tbl:ukb} and \Cref{fig:ukb}),
we see that ADP, which is the most reliable method,
is the slowest in study runtimes.
By using the online SVD algorithm,
OADP achieved the highest accuracy (excluding ADP, which is the golden standard) and the fastest runtime.
SP is fast, also,
but its accuracy is the lowest.
By using the HDPCA package,
AP reduces the error of AP
and achieved the second highest in accuracy.
The randomized version of SP is as accurate as the standard SP,
which shows that the randomized SVD algorithm gives reliable results,
and that using linear regression to predict the uncalculated reference eigenvalues is satisfactory.
It also reduces the runtime almost by half,
due to not calculating all the eigenvalues.
Similar reduction in study runtime is observed for the randomized version of AP,
but in this case the accuracy is also decreased,
thought it is still higher than that of SP and RSP.
Finally, the randomized OADP is disappointing,
as its error is almost as high as SP and RSP.

The pattern for accuracy is very similar when we look at the simulated data.
(\Cref{tbl:nChg-runtimes-ref}, \Cref{tbl:nChg-runtimes-study},
\Cref{tbl:nChg-accuracy-gold}, \Cref{tbl:nChg-accuracy-ctr},
\Cref{tbl:mChg-runtimes-study}).
A noticeable difference in this case is the accuracy of ROADP.
Here ROADP's accuracy is almost identical to OADP's,
as measured by both the golden standard error and the geographic center err.
However, as the reference size increases,
the accuracies of different methods become closer and closer (\Cref{fig:nChg}).
As for the speed,
AWD's study runtime increases so fast with the reference size
that the study runtimes for the other methods seem to be constant in comparison (\Cref{fig:nChg}).
On the other hand,
the study runtimes appear to increase linearly with respect to the study size (\Cref{fig:mChg}).
This information can be used to predict the runtime for larger study samples.

@@

In addition to estimating the PC scores of the study individuals,
we have another algorithm that aims at improving the decomposition of the
training data.
For SP, AP, ADP, and OADP, we need to find the covariance matrix of the training
data, which has dimension $n \times n$, and conduct eigendecomosition on it.
However, when $n$ is exceedingly large,
computation and memory cost of PCA on the reference samples can be enormous.
A randomized SVD (RSVD) algorithm has been developed to handle this issue.
When the reference sample size is small, RSVD can be slower than standard SVD,
but it is scalable to large sample size.
For the details of the RSVD algorithm, see \citet{halko2011finding}.

Notice that the randomized SVD method on the training data
only calculates the first $k$ eigenvalues.
However, in order to use adjusted projection,
all the eigenvalues of the training data are required.
Thus for the missing eigenvalues,
we predict them by regressing their log-scale values on the ranks
and using the first $k$ eigenvalues for training the linear regression.

@@

\bibliographystyle{plainnat}
\bibliography{frugalpca}

@@

\begin{table} 
  \centering
  \begin{tabular}{|l|l|l|}
    \hline
    Method & Reference Complexity & Study Complexity \\ 
    \hline
    ADP & $\bO[n^2 p]$ & $\bO[mn(p + n^2)]$ \\
    \hline
    OADP & $\bO[n^2 p]$ & $\bO[mk(p + k n)]$ \\
    \hline
    ROADP & $\bO[k^2 p]$ & $\bO[mk(p + k n)]$ \\
    \hline
    SP & $\bO[n^2p]$ & $\bO[mkp]$ \\
    \hline
    RSP & $\bO[k^2p]$ & $\bO[mkp]$ \\
    \hline
    AP & $\bO[n^2p]$ &  $\bO[mkp]$ \\
    \hline
    RAP & $\bO[k^2p]$ &  $\bO[mkp]$ \\
    \hline
  \end{tabular}
  \caption{
    Comparison of computational complexity for different methods.
    Here $p$ is the number of SNPs,
    $n$ is the number of individuals in the reference group,
    $m$ is the number of individuals in the  study group,
    and $k$ is the number of PCs calculated by the corresponding method.
  }
  \label{tbl:cplx}
\end{table}

\begin{table} 
  \centering
  \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & Reference Runtimes (n=?) & Study Runtimes (m=?)& Golden Standard Error \\ 
    \hline
    ADP & 411 & 29813 & 0.00 \\
    \hline
    OADP & 2518 & 103 & 0.40 \\
    \hline
    ROADP & 2518 & 103 & 1.93 \\
    \hline
    SP & 411 & 425 & 1.95 \\
    \hline
    RSP & 2504 & 241 & 1.95 \\
    \hline
    AP & 411 & 482 & 1.12 \\
    \hline
    RAP & 2505 & 250 & 1.83 \\ 
    \hline
  \end{tabular}
  \caption{
    Comparison of runtimes and accuracy for different methods applied to the real-life datasets.
    The reference individuals are from the 1000 Genomes dataset with 2492 unrelated individuals.
    The study sample contain 1000 individuals from the UKBioBank dataset.
    There are about 125,000 loci shared by the reference and study data.
    The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
  }
  \label{tbl:ukb}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        &  68  & 1263 & 2871 & 5720 & 9737 \\
    OADP       &  72  & 18   & 19   & 22   & 24   \\
    ROADP      & 809  & 18   & 17   & 20   & 21   \\
    SP         &  68  & 26   & 42   & 67   & 96   \\
    RSP        & 805  & 23   & 31   & 39   & 46   \\
    AP         &  68  & 69   & 107  & 91   & 119  \\
    RAP        & 805  & 11   & 24   & 29   & 9    \\
    \hline
  \end{tabular}
  \caption{
    Reference runtimes for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-runtimes-ref}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 391  &  130 &  222 &  339 &  486 \\
    OADP       & 15   &  136 &  230 &  350 &  499 \\
    ROADP      & 15   & 1211 & 1633 & 2023 & 2422 \\
    SP         & 16   &  130 &  222 &  339 &  486 \\
    RSP        & 15   & 1204 & 1624 & 2012 & 2409 \\
    AP         & 34   &  130 &  222 &  339 &  486 \\
    RAP        & 18   & 1204 & 1624 & 2012 & 2409 \\
    \hline
  \end{tabular}
  \caption{
    Study runtimes for simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-runtimes-study}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Study Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 0.00  & 0.00 & 0.00 & 0.00 & 0.00 \\
    OADP       & 0.23  & 0.15 & 0.11 & 0.08 & 0.07 \\
    ROADP      & 0.23  & 0.15 & 0.12 & 0.08 & 0.08 \\
    SP         & 6.00  & 4.34 & 3.43 & 2.75 & 2.34 \\
    RSP        & 6.00  & 4.34 & 3.43 & 2.75 & 2.34 \\
    AP         & 0.46  & 0.37 & 0.31 & 0.26 & 0.22 \\
    RAP        & 3.02  & 2.93 & 2.54 & 2.15 & 1.91 \\
    \hline
  \end{tabular}
  \caption{
    Golden standard error for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-accuracy-gold}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 4.53  & 4.13 & 3.81 & 3.59 & 3.23 \\
    OADP       & 4.43  & 4.06 & 3.77 & 3.55 & 3.20 \\
    ROADP      & 4.44  & 4.06 & 3.76 & 3.55 & 3.20 \\
    SP         & 5.79  & 4.51 & 3.89 & 3.56 & 3.19 \\
    RSP        & 5.79  & 4.51 & 3.89 & 3.56 & 3.19 \\
    AP         & 4.59  & 4.10 & 3.76 & 3.57 & 3.24 \\
    RAP        & 4.23  & 3.87 & 3.55 & 3.38 & 3.07 \\
    \hline
  \end{tabular}
  \caption{
    Geographic center error for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-accuracy-ctr}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 507  & 758 & 1011 & 1262 & 1549 \\
    OADP       &  73  & 108 &  156 &  189 &  282 \\
    ROADP      &  73  & 108 &  159 &  183 &  281 \\
    SP         &  44  &  64 &   84 &  103 &  131 \\
    RSP        &  43  &  63 &   83 &  101 &  129 \\
    AP         &  66  &  81 &  100 &  117 &  146 \\
    RAP        &  22  &  15 &   15 &   21 &   24 \\
    \hline
  \end{tabular}
  \caption{
    Study runtimes for the simulated data as the study size increases.
    The reference size is fixed to 600 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:mChg-runtimes-study}
\end{table}

>>>>

\usepackage{epsfig} \usepackage[margin=1.5in]{geometry}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[capitalise]{cleveref}
\usepackage{verbatim}
\usepackage{float}
\usepackage{graphicx}

@@

We also applied the four methods
to study the UK Biobank data \citep{sudlow2015uk},
which consists of 490,000 middle- or elderly-aged individuals
in the United Kingdom.
Our reference samples
are from the 1000 Genomes Project \citep{10002015global},
which collected 2500 samples from Europe, Africa, East Asia, South Asia, and America.
(Individuals whose children are also in the data were removed.)
The reference and the study samples
have 145,000 SNPs in common.
After we predicted the PC scores and ethnic groups
of the study samples,
we selected the study samples predicted to by Europeans
and applied PCA to them
by using the European reference samples only.
Since ADP is very slow compared to the other three methods,
we randomly selected 500 study samples
and used them to compare the four methods.
After that,
we applied SP, AP, and OADP to all the study samples.

@@

\subsection{Simulation study}

% Runtimes vs ref size
% Distance to ADP vs ref size
% Distance to geo center vs ref size
% PC1 vs PC2, 5 x 3 grid (uncolored study samples)
% The predicted PC scores are shown in \Cref{fig:n1000} and \Cref{fig:ukb}.

For the simulation study
(\Cref{tbl:nChg-runtimes-ref}, \Cref{tbl:nChg-runtimes-study},
\Cref{tbl:nChg-accuracy-gold}, \Cref{tbl:nChg-accuracy-ctr},
\Cref{tbl:mChg-runtimes-study}),
we see that ADP, which is the most reliable method,
is the slowest in study runtimes.
By using the online SVD algorithm,
OADP achieved the highest accuracy (excluding ADP, which is the golden standard) and the fastest runtime.
SP is fast, also,
but its accuracy is the lowest.
By using the HDPCA package,
AP reduces the error of SP
and achieved the second highest in accuracy.
However, as the reference size increases,
the accuracies of different methods become closer and closer (\Cref{fig:nChg}).
As for the speed,
ADP's study runtime increases so fast with the reference size
that the study runtimes for the other methods seem to be constant in comparison (\Cref{fig:nChg}).
On the other hand,
the study runtimes appear to increase linearly with respect to the study size (\Cref{fig:mChg}).
This information can be used to predict the runtime for larger study samples.

\subsection{UK Biobank data}

When we used the global samples,
we found that the PC scores predicted by the four methods' are almost identical.
The separation of the ethnic groups was clear,
and the shrinkage bias of SP was not obvious,
which is consistent with the theoretical understanding
that the shrinkage bias decreases
as the signal-to-noise ratio increases.

However, when we focus on the European (EUR) samples only,
the results given by SP were clearly unreliable.
The samples from British in England and Scotland (GBR)
and those from Utah residents with northern and western European ancestry	(CEU)
drifted very close to NULL.
This causes SP to incorrectly classified almost all of them as CEU,
since most GBR reference samples are far away from NULL.
A few of the study samples predicted by ADP to be GBR or CEU
were even classified as the Iberian population in Spain (IBS),
since the IBS reference samples are close to NULL.
Moreover, the shrinkage for the IBS
and for the Toscani in Italia (TSI) populations
caused significant errors within these two groups.
The IBS reference samples
are approximately in the middle
between the TSI reference samples and NULL.
Thus most of the the study samples predicted by ADP to be TSI
were classified by SP as IBS.

For OADP, its predicted PC1 and PC2 scores
for the European study samples
are almost identical
to those done by ADP.
OADP's results for PC3 and PC4
are also very close to ADP's results,
though we observed a very slight decrease in the magnitude of the PC scores.
This minor shrinkage did not affect
OADP's classification for the IBS and TSI samples,
since their PC1 and PC2 scores were accurately predicted by OADP.
Neither was any CEU/GBR sample classified as IBS/TSI. 
For the CEU and GBR samples,
their predicted PC scores are tightly mixed together
for all the 4 PCs,
which were even difficult for ADP to separate them.
Thus the slight difference in PC3 and PC4 scores
between OADP and ADP
caused the classification of many CEU and GBR samples
to be different on the two methods.

Furthermore, AP successfully adjusted for the shrinkage
in PC1 and PC2 for the European samples,
so its predicted PC scores are almost identical to ADP's.
However, it did not detect the shrinkage in PC 3 and PC4,
so its predicted PC scores are the same as SP's for these two PCs.
This still allowed AP to correctly separate
the CEU/GBR samples from the IBS/TSI samples.
However, its separation of the IBS and TSI samples
did not agree completely with that done by ADP,
most likely caused by the shrinkage on PC3.
For the classification between CEU and GBR,
the AP's results differ far from ADP's,
as AP classified many more CEU/GBR samples as CEU.

The patterns for the accuracy of SP, AP, and OADP
discussed above
were also observed
when we used all the 490,000 study samples in the UK Biobank dataset
and those predicted to be Europeans among them.
See \Cref{tbl:ukb} for details.

@@

For the future, we would like
to improve the parallelization of our software.
Currently it uses the poor-man’s parallelism,
that is,
dividing the study dataset into multiple smaller files on the hard drive,
applying the analysis to each of them,
and merge the results.
This parallelism saves both the memory usage and the runtime.
However, we would like to utilize
more sophisticated parallel computation techniques
to further improve the performance of our software.

@@

% In addition to estimating the PC scores of the study individuals,
% we have another algorithm that aims at improving the decomposition of the
% training data.
% For SP, AP, ADP, and OADP, we need to find the covariance matrix of the training
% data, which has dimension $n \times n$, and conduct eigendecomosition on it.
% However, when $n$ is exceedingly large,
% computation and memory cost of PCA on the reference samples can be enormous.
% A randomized SVD (RSVD) algorithm has been developed to handle this issue.
% When the reference sample size is small, RSVD can be slower than standard SVD,
% but it is scalable to large sample size.
% For the details of the RSVD algorithm, see \citet{halko2011finding}.

% Notice that the randomized SVD method on the training data
% only calculates the first $k$ eigenvalues.
% However, in order to use adjusted projection,
% all the eigenvalues of the training data are required.
% Thus for the missing eigenvalues,
% we predict them by regressing their log-scale values on the ranks
% and using the first $k$ eigenvalues for training the linear regression.

@@

\bibliographystyle{plainnat}
\bibliography{paper}

@@

\begin{table} 
  \centering
  \begin{tabular}{|l|l|l|}
    \hline
    Method & Reference Complexity & Study Complexity \\ 
    \hline
    ADP & $\bO[n^2 p]$ & $\bO[mn(p + n^2)]$ \\
    \hline
    OADP & $\bO[n^2 p]$ & $\bO[mk(p + k n)]$ \\
    \hline
    SP & $\bO[n^2p]$ & $\bO[mkp]$ \\
    \hline
    AP & $\bO[n^2p]$ &  $\bO[mkp]$ \\
    \hline
  \end{tabular}
  \caption{
    Comparison of computational complexity for different methods.
    Here $p$ is the number of SNPs,
    $n$ is the number of individuals in the reference group,
    $m$ is the number of individuals in the  study group,
    and $k$ is the number of PCs calculated by the corresponding method.
  }
  \label{tbl:cplx}
\end{table}

\begin{table} 
  \centering
  \begin{tabular}{|l|l|l|l|l|}
    \hline
    Method & Reference Runtimes (n=2492) & Study Runtimes (m=1000)& Golden Standard Error \\ 
    \hline
    ADP & 411 & 29813 & 0.00 \\
    \hline
    OADP & 2518 & 103 & 0.40 \\
    \hline
    SP & 411 & 425 & 1.95 \\
    \hline
    AP & 411 & 482 & 1.12 \\
    \hline
  \end{tabular}
  \caption{
    Comparison of runtimes and accuracy for different methods applied to the real-life datasets.
    The reference individuals are from the 1000 Genomes dataset with 2492 unrelated individuals.
    The study sample contain 1000 individuals from the UKBioBank dataset.
    There are about 125,000 loci shared by the reference and study data.
    The golden standard error is the square root of the averate squared distance between the study individuals' PC scores predicted by different methods compared to the golden standard result, which in our case is the PC scores predicted by ADP.
  }
  \label{tbl:ukb}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        &  68  & 1263 & 2871 & 5720 & 9737 \\
    OADP       &  72  & 18   & 19   & 22   & 24   \\
    SP         &  68  & 26   & 42   & 67   & 96   \\
    AP         &  68  & 69   & 107  & 91   & 119  \\
    \hline
  \end{tabular}
  \caption{
    Reference runtimes for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-runtimes-ref}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 391  &  130 &  222 &  339 &  486 \\
    OADP       & 15   &  136 &  230 &  350 &  499 \\
    SP         & 16   &  130 &  222 &  339 &  486 \\
    AP         & 34   &  130 &  222 &  339 &  486 \\
    \hline
  \end{tabular}
  \caption{
    Study runtimes for simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-runtimes-study}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Study Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 0.00  & 0.00 & 0.00 & 0.00 & 0.00 \\
    OADP       & 0.23  & 0.15 & 0.11 & 0.08 & 0.07 \\
    SP         & 6.00  & 4.34 & 3.43 & 2.75 & 2.34 \\
    AP         & 0.46  & 0.37 & 0.31 & 0.26 & 0.22 \\
    \hline
  \end{tabular}
  \caption{
    Golden standard error for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-accuracy-gold}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000  & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 4.53  & 4.13 & 3.81 & 3.59 & 3.23 \\
    OADP       & 4.43  & 4.06 & 3.77 & 3.55 & 3.20 \\
    SP         & 5.79  & 4.51 & 3.89 & 3.56 & 3.19 \\
    AP         & 4.59  & 4.10 & 3.76 & 3.57 & 3.24 \\
    \hline
  \end{tabular}
  \caption{
    Geographic center error for the simulated data as the reference size increases.
    The study size is fixed to 200 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:nChg-accuracy-ctr}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    ADP        & 507  & 758 & 1011 & 1262 & 1549 \\
    OADP       &  73  & 108 &  156 &  189 &  282 \\
    SP         &  44  &  64 &   84 &  103 &  131 \\
    AP         &  66  &  81 &  100 &  117 &  146 \\
    \hline
  \end{tabular}
  \caption{
    Study runtimes for the simulated data as the study size increases.
    The reference size is fixed to 600 and the number of SNPs is 100,000 (1000 per genealogy). 
    Simulation is done on a $2 \times 2$ grid with a migration rate of 100 by the GGS software. 
  }
  \label{tbl:mChg-runtimes-study}
\end{table}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_sp}
  \caption{EUR samples in UK Biobank data by SP}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_ap}
  \caption{EUR samples in UK Biobank data by AP}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_oadp}
  \caption{EUR samples in UK Biobank data by oadp}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{ukb_snpscap_kgn_bial_orphans_5c_pred_EUR_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_EUR_adp}
  \caption{EUR samples in UK Biobank data by adp}
\end{figure}
